### 2021-04-17 manuscript.rmd
downgrade the author argument to a footnote

This study of ecological effect on individual behaviors has a long tradition in social sciences. A famous example was Émile Durkheim's investigation on the ecological factors associated with suicide [@durkheim1897suicide]. Durkheim found the higher suicide rate among citizens from Scandinavian countries than those from other European countries. Using today’s standard, Durkheim's analysis is descriptive and this descriptive approach for studying ecological effect is indeed still useful for hypothesis generation in comparative research. An example of hypothesis-generating comparative research is @chan2020combining, in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized. Hypothesis-generating comparative study, however, is rare. Most studies have a confirmatory outlook. As we see from the example hypotheses above, most of these studies propose hypotheses to test for ecological effects. In this context usually traditional (frequentist) hypothesis testing approaches were used: @esser:2013:C lumped multiple outlets from the same country together and then used univariate analysis of variance to test for the differences in the proportion of opinion-orienting articles across countries. In @wu:2000:SDI, multiple stepwise regression was used. These approaches violate the underlying assumptions of the statistical analyses. It highlights the fact that comparative research introduces a feature that researchers usually overlook: media contents are clustered in multilevel. A news article is nested within its media outlet and its media outlet is in turn nested within its country. Theoretically with a large enough sample it can be argued that a news article is nested within authors. Such data structure brings two problems: non-atomicity and non-stochasticity.

>>>>

This study of ecological effect on individual behaviors has a long tradition in social sciences. A famous example was Émile Durkheim's investigation on the ecological factors associated with suicide [@durkheim1897suicide]. Durkheim found the higher suicide rate among citizens from Scandinavian countries than those from other European countries. Using today’s standard, Durkheim's analysis is descriptive and this descriptive approach for studying ecological effect is indeed still useful for hypothesis generation in comparative research. An example of hypothesis-generating comparative research is @chan2020combining, in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized. Hypothesis-generating comparative study, however, is rare. Most studies have a confirmatory outlook. As we see from the example hypotheses above, most of these studies propose hypotheses to test for ecological effects. In this context usually traditional (frequentist) hypothesis testing approaches were used: @esser:2013:C lumped multiple outlets from the same country together and then used univariate analysis of variance to test for the differences in the proportion of opinion-orienting articles across countries. In @wu:2000:SDI, multiple stepwise regression was used. These approaches violate the underlying assumptions of the statistical analyses. It highlights the fact that comparative research introduces a feature that researchers usually overlook: media contents are clustered in multilevel. A news article is nested within its media outlet and its media outlet is in turn nested within its country [^author]. Such data structure brings two problems: non-atomicity and non-stochasticity.

[^author]: Theoretically with a large enough sample it can be argued that a news article is nested within authors.
